---
title: "Getting Started with cointoss"
author: "Gaston Sanchez"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to cointoss}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
```

## Binomial

The package `"binomial"` is an implementation for simulating binomial distributions given a number of trials and probability. 

## Binomial Choose

Given a number of trials and number of successes, this will return the number of combinations there are
```{r}
bin_choose(5,2)
```

## Binomial Probability

Given a number of trials, successes and probability of success, this will return the probability of given successes in given number of trials.
```{r}
bin_probability(2,5,0.5)
```

## Binomial Distribution

Given a number of trials and probability, this returns a dataframe with all distributions across successes. The plot of this distribution can also be retrieved.
```{r}
x <- bin_distribution(10, 0.5)
x
plot(x)
```

## Binomial Cumulative

This gives the cumulative probability distribution given a certain number of trials and probability. The plot of this distribution can also be retrieved.
```{r}
y <- bin_cumulative(10, 0.5)
y
plot(y)
```

## Binomial Variable

This creates a binomial variable that we can then extract stats from.
```{r}
var <- bin_variable(10, 0.5)
var
summary(var)
```
